The Astropy Project

### 2017-11-13 main.tex
future

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing set up
and installation process for various continuous integration services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

@@

\section{The future of the Astropy project}
\label{sec:future}
% First draft by SMC
% edited by BMS

%\inlinecomment{PLL}{In addition to PY3, add some killer features that we
%  plan to implement for 3.0 and beyond?}
%\inlinecomment{BMS}{Some killer features we already know about to definitely
%have may be mentioned here. e.g. functionality of astropy-healpix? or the
%performance/speedup focus of the 3.1 release?}
\inlinecomment{BMS}{should we mention the refactored infra here?
  e.g. pytest-astropy and sphinx-astropy?}
%\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
%
\par Development has already been continued after the release of v2.0 of
\astropypkg. The most significant development for the next release will
be removing python 2 support \citep{ape10}, the v3.0 \astropypkg release
will only support python 3.  This will allow the use of the new
functionality in python 3, simplify the code base, and reducing the
testing overhead.   The v3.0 release is currently scheduled for January
2018.
%
\par In the next major release after v3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation. To prepare for this release, software for testing and
monitoring the performance of the code are being developed.   Less
functionality may be introduced in this release while the focus will be
primarily on improved performance.  In addition, a new suite of tutorials
and documentation are being prepared for this release.
%
\par Beyond the core code, the \astropy project is also further
developing the affiliated packages.  This includes elevating a suite of
packages into part of the core project. While these may not be integrated
into the \astropypkg core code, these projects provide code that is
useful to the astronomical community and meet the testing and
documentation standards of \astropy.   Some of these new efforts includes
an initiative to develop tools for spectroscopy
\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX
projection% \citep{astropy-healpix}
.
\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
\subsection{Learn Astropy}
% Adrian

>>>>

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing set up
and installation process for various continuous integration services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

@@

\section{The future of the Astropy project}
\label{sec:future}
% First draft by SMC
% edited by BMS
% edited again by Adrian PW

Following the release of version 2.0, development on the next major version of
the \astropypkg core package (version 3.0) has already begun.
On top of planned changes and additions to the core package, we also plan to
overhaul the \astropy educational and learning materials, and further refactor
and generalize the infrastructure utilities developed for the core package for
the benefit of the community.

\inlinecomment{BMS}{should we mention the refactored infra here?
  e.g. pytest-astropy and sphinx-astropy?}

\subsection{Future versions of the \astropypkg core package}

One of the most significant changes coming in this next major release will be
removing support for \python 2 \citep{ape10}: future versions of \astropypkg
will only support \python 3.5 and higher.
Removing \python 2 support will allow the use of new, \python 3-only features,
will simplify the code base, and reduce the testing overhead for the package.
\astropypkg version 3.0 is currently scheduled for January 2018.

\par In the next major release after v3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation. To prepare for this release, software for testing and
monitoring the performance of the code are being developed.   Less
functionality may be introduced in this release while the focus will be
primarily on improved performance.  In addition, a new suite of tutorials
and documentation are being prepared for this release.
%
\par Beyond the core code, the \astropy project is also further
developing the affiliated packages.  This includes elevating a suite of
packages into part of the core project. While these may not be integrated
into the \astropypkg core code, these projects provide code that is
useful to the astronomical community and meet the testing and
documentation standards of \astropy.   Some of these new efforts includes
an initiative to develop tools for spectroscopy
\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX
projection% \citep{astropy-healpix}
.
\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}

\subsection{Learn Astropy}
% Adrian
